Simulation Results

### 2020-05-10 Simulation Results/Simulation Results.Rmd

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache = TRUE)
theme_set(theme_minimal())
library(magrittr)
library(here)
```

@@

```{r}
exp_gamma_acc_files <- c(
  here("Simulation Results", "simple-models", "continuous", "exponential", "gamma-prior", "exponential-gamma-accuracy.rds"),
  here("Simulation Results", "simple-models", "continuous", "exponential", "gamma-prior", "exponential-gamma-accuracy-nimble.rds")
)

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache = TRUE)
library(tidyverse); options(tibble.width = Inf)
library(magrittr)
theme_set(theme_minimal())
library(here)
```

@@

```{r}
readRDS(here("Simulation Results", "simple-models", "continuous", "exponential", "gamma-prior", "exponential-gamma-accuracy.rds"))

exp_gamma_acc_files <- c(
  here("Simulation Results", "simple-models", "continuous", "exponential", "gamma-prior", "exponential-gamma-accuracy.rds"),
  here("Simulation Results", "simple-models", "continuous", "exponential", "gamma-prior", "exponential-gamma-accuracy-nimble.rds")
)
